---
title: "Cancer Prediction Case Study"
author: "Mia Brito"
date: "4/14/2022"
output:
  pdf_document: default
---



## Executive Summary

## The Probelm
For this case, we must find the best model for predicting the 
## Related Literature

## Methodology

## Data Analysis

\newpage

##Appendix

id: Patient ID number
diagnosis: Diagnosis (M = malignant, B = benign)
3-32 Ten real-valued features are computed for each cell nucleus:
a) radius (mean of distances from center to points on the
perimeter)
b) texture (standard deviation of gray-scale values)
c) perimeter
d) area
e) smoothness (local variation in radius lengths)
f) compactness (perimeter^2 / area - 1.0)
g) concavity (severity of concave portions of the contour)
h) concave points (number of concave portions of the contour)
i) symmetry
j) fractal dimension ("coastline approximation" - 1)

## Loading In Libraries

```{r library,message=FALSE,echo = TRUE}
library(tidyverse)
library(readr)
library(readxl)
library(caret)
library(caTools)
library(ROCR)
library(corrplot)
source('/Users/admin/Desktop/optim_threshold.R')
```

## Reading in Data

```{r}
b1 <- read.csv("/Users/admin/Desktop/CancerData.csv", sep = ",")
```

## Make Factor variables

```{r}
b1$diagnosis = as.factor(b1$diagnosis)
str(b1)
```

## Removing Highly Correlated Values
```{r}
b1_num = dplyr::select_if(b1, is.numeric)
M = cor(b1_num)
highcorr = findCorrelation(M, cutoff = .9, names = TRUE)
b1 = dplyr::select(b1, - highcorr)
```

## Splitting data into Training and Testing
```{r}
set.seed(1)
tr_ind = sample(nrow(b1),.8*nrow(b1), replace = F)
b1train = b1[tr_ind,]
b1test = b1[-tr_ind,]
```

### Check correlation in variables

```{r}
b1_num = dplyr::select_if(b1, is.numeric)
M = cor(b1_num)
corrplot(M, method = "circle")
b1 = dplyr::select(b1, - concave.points_worst)
```

##Plots

```{r}
ggplot(b1, aes(x = area_mean, fill = diagnosis)) +
  geom_histogram(position = "identity", alpha = 0.4)

ggplot(b1, aes(x = radius_se, fill = diagnosis)) +
  geom_histogram(position = "identity", alpha = 0.4)

ggplot(b1, aes(x = texture_worst, fill = diagnosis)) +
  geom_histogram(position = "identity", alpha = 0.4)

ggplot(b1) +
  aes(x = diagnosis, fill = diagnosis, colour = diagnosis) +
  geom_bar() +
  scale_fill_viridis_d(option = "cividis", direction = 1) +
  scale_color_viridis_d(option = "cividis", direction = 1) +
  labs(
    x = "Diagnosis (B or M)",
    y = "Count",
    title = "Cancer Diagnosis"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20L,
    hjust = 0.5),
    axis.title.y = element_text(size = 13L),
    axis.title.x = element_text(size = 13L)
  )


```



```{r}
colSums(is.na(b1))
```


```{r}
a1 = glm(formula = diagnosis ~ ., data = b1 , family = binomial)


car::vif(a1)
summary(a1)

predprob = predict.glm(a1, newdata = b1test, type = "response")
predclass_log = ifelse(predprob >= .36, "M", "B")
caret::confusionMatrix(as.factor(predclass_log), as.factor(b1test$diagnosis), positive = "M")

```

```{r}
optim_threshold(a1,b1, b1$diagnosis)
```


### Use Step function to reduce variables

```{r}
m2.log = step(a1, direction = "backward")
summary(m2.log)

car::vif(m2.log)
```



