---
title: "Cancer Prediction Case Study"
author: "Mia Brito"
date: "4/14/2022"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive Summary

## The Probelm
For this case, we must find the best model for predicting the 
## Related Literature

## Methodology

## Data Analysis

\newpage

##Appendix

id: Patient ID number
diagnosis: Diagnosis (M = malignant, B = benign)
3-32 Ten real-valued features are computed for each cell nucleus:
a) radius (mean of distances from center to points on the
perimeter)
b) texture (standard deviation of gray-scale values)
c) perimeter
d) area
e) smoothness (local variation in radius lengths)
f) compactness (perimeter^2 / area - 1.0)
g) concavity (severity of concave portions of the contour)
h) concave points (number of concave portions of the contour)
i) symmetry
j) fractal dimension ("coastline approximation" - 1)

## Loading In Libraries

```{r library,message=FALSE,echo = TRUE}
library(tidyverse)
library(readr)
library(readxl)
library(caret)
library(caTools)
source('/Users/admin/Desktop/optim_threshold.R')
```

## Reading in Data

```{r}
b1 <- read.csv("/Users/admin/Desktop/CancerData.csv", sep = ",")
```

## Make Factor variables

```{r}
b1$diagnosis = as.factor(b1$diagnosis)
str(b1)
```

## Removing Highly Correlated Values
```{r}
b1_num = dplyr::select_if(b1, is.numeric)
M = cor(b1_num)
highcorr = findCorrelation(M, cutoff = .9, names = TRUE)
b1 = dplyr::select(b1, - highcorr)
```

## Splitting data into Training and Testing
```{r}
split = sample.split(b1$diagnosis, SplitRatio = 0.8)
b1train = subset(b1, split == TRUE)
b1test = subset(b1, split == FALSE)
```


```{r}
